Distributed Decision Making for Dynamic Formation of Web Services Communities

### 2015-01-16 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

%\begin{figure*}%[!t]
%\centerline{\includegraphics[width=6.25in]{figures/community.eps}}
%\caption{Architecture of web service communities}
%\label{fig_community}
%\end{figure*}

@@

Now, we want to generate a set of feature vectors representing the communities of web services for training purposes. For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services. Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services. $C = {ws_1,...ws_k}$. The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly. A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set. We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.

>>>>

@@

\begin{figure}%[!t]
\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
\label{fig_community}
\end{figure}

Now, we want to generate a set of feature vectors representing the communities of web services for training purposes. For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services. Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services. $C = {ws_1,...ws_k}$. The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly. A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set. We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}. Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
